### 2015-07-10 narrative/intro.tex
changed from manish, as well as other minor changes.

\paragraph{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of reading, this project will look at both
CR  and post-processing I/O patterns. For the former case,
we will allow both traditional file-based approach leveraging fast storage tier
such as NVRAM (non-volatile RAM), and memory-based approach via retrieving
data directly from NVRAM. For the latter case,
an important aspect is that they want a reduction of latency and they
require a certain amount of QoS as well. When someone is
doing interactive analysis and expects that the data they read in is about
10s, but it turns into 1,000s, the user typically tends to either wait
another day for doing their analysis or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data~\S\ref{sec:migration}.

>>>>

\paragraph{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of reading, this project will look at key I/O patterns such as checkpoint-restart (CR), in-situ analytics and post-processing. 
For example, in case of CR, we will support both, traditional file-based approaches leveraging fast storage tiers
such as NVRAM (non-volatile RAM), as well as memory-based approach based on retrieving
data directly from NVRAM. In case of in-situ and post-processing,  an important aspect is the latency -- here reducing latency and providing QoS 
 becomes important. 
 When someone is doing interactive analysis and expects that the data they read in is about
10s, but it turns into 1,000s, the user typically tends to either wait
another day for doing their analysis or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data~\S\ref{sec:migration}.

### 2015-07-10 narrative/proposed-work.tex
changed from manish, as well as other minor changes.

Additionally we recognize that HPC applications exhibit a set
of common I/O patterns \cite{lofstead2011six,polte2009and,tian2011edo,tian2012system},
Throughout our project we will continuously focus on creating research artifacts 
which can optimize these I/O patterns on current and
exascale systems. One important pattern is Checkpoint/Restart (C/R) and we will focus on optimizing this pattern,
 and also using many of the important research techniques for using NVRAM and neighbor's NVRAM for storing and retrieving
the C/R data. The migration and purging of this will be optimized by our SSIO layer using the utility function of the C/R data so that this can be stored for short periods of time, and then purged.

>>>>

Additionally we recognize that HPC applications exhibit a set
of common I/O patterns \cite{lofstead2011six,polte2009and,tian2011edo,tian2012system}.
Throughout our project we will continuously focus on creating research artifacts 
which can optimize these I/O patterns on current and
exascale systems. One key focus is Checkpoint/Restart (C/R), leveraging NVRAM to accelerate
checkpoint and data retrieval. 
The migration and purging of this will be optimized by SIRUS using the utility function of 
the C/R data so that this can be stored for short periods of time, and then purged.
